On-the-fly Algorithms for GKAT Equivalences \thanks{Identify applicable funding agency here. If none, delete this.}

### 2025-01-13 main.tex
ok

Although the size of the coalgebra generated by the derivative is smaller than Thompson's construction, the decision procedure based on derivative is not always more efficient than those based on Thompson's construction. 
Crucially, the states in the derivative coalgebra \(D̂\) are expressions, which is more expensive to store; and computing the next transition of the coalgebra can also be more computationally expensive.
Whereas, Thompson's construction only requires inductively going through the expression once to construct the entire coalgebra \(Ŝ_{e}\), and its states can be represented by more efficient constructs, like integers.

@@

>>>>

Although the size of the coalgebra generated by the derivative is smaller than Thompson's construction, the decision procedure based on derivative is not always more efficient than those based on Thompson's construction. 
Crucially, the states in the derivative coalgebra \(D̂\) are expressions, which are more expensive to store; and computing the next transition of the coalgebra can also be more computationally expensive.
Whereas, Thompson's construction only requires inductively going through the expression once to construct the entire coalgebra \(Ŝ_{e}\), and its states can be represented by more efficient constructs, like integers.

@@

As mentioned in \Cref{sec:symb-gkat-construction}, our implementation of Thompson's construction uses start dynamics (pseudo-state) instead of an explicit start state. This reduces the number of indirections needed to access the behaviors \(\hat{\epsilon}(s^*) \) and \(\hat{\delta}(s^*)\) of start state \(s^*\). More specifically, we track the behaviors \(\epsilon^*\) and \(\delta^*\) which characterize \(\hat{\epsilon}(s^*) \) and \(\hat{\delta}(s^*)\) respectively. The start state \(s^*\) does not appear explicitly during coalgebra construction. After the construction algorithm terminates, we generate a fresh state \(s^*\) and set \(\hat{\epsilon}(s^*) = \epsilon^*\) and \(\hat{\delta}(s^*) = \delta^*\). The final coalgebra that our implementation produces is equivalent to what would have been obtained from the original algorithm (\Cref{tab:symb-Thompson-construction}) modulo consistent renaming of states.
